\renewcommand{\abstractname}{\vspace{-\baselineskip}}
\begin{abstract}
    Edge computing is a promising technique for the increasing time-sensitive and computation-intensive tasks at the mobile devices.
    Multiple access points (APs) are deployed to collect jobs from the mobile users (MUs), and upload each job to the edge servers.
    The edge computing network connecting APs and edge servers is considered residing in a Metropolitan Area Network (MAN), where the transmission and propagation delays are all random due to unexpected network traffics generated from other services.
    Moreover, to facilitate the distributed cooperation of job dispatching at all APs, the signaling model is designed that APs and edge servers periodically broadcast their local state information.
    The signaling latency of broadcast information is also random, and the APs should apply job dispatching strategies according to outdated and partially observable broadcast information.
    In this work, the problem of distributed optimization of job dispatching strategies at all APs is formulated as a partially observable Markov decision process (POMDP), whose minimization objective is a discount measurement of job delivery and computation time.
    While conventional solution for POMDP is impractical due to huge complexity, a novel low-complexity solution framework is proposed to address the issue of algorithm complexity.
    Based on it, the optimization of job dispatching strategy can be decoupled via an alternative action update algorithm, so that the distributed policy iteration of each AP can be made according to the partially observable system state information.
    Finally, an analytical performance lower bound is provided.
\end{abstract}
